Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-27 1_manuscript/itt-emotion.tex
Restored from sep 24 2020 morning

  \usepackage{lineno, hyperref}
  \usepackage{array, pbox}
  \usepackage{mathtools}
  \usepackage{caption}
  \usepackage{graphicx}

@@

  % To add hypothesis theorem
  \usepackage{ntheorem}
  \theoremseparator{:}
  \newtheorem{hyp}{Hypothesis}

  % To add subhypothesis theorems
  \makeatletter
  \newcounter{subhyp} 
  \let\savedc@hyp\c@hyp
  \newenvironment{subhyp}
   {%
    \setcounter{subhyp}{0}%
    \stepcounter{hyp}%
    \edef\saved@hyp{\thehyp}% Save the current value of hyp
    \let\c@hyp\c@subhyp     % Now hyp is subhyp
    \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
   }
   {}
  \newcommand{\normhyp}{%
    \let\c@hyp\savedc@hyp % revert to the old one
    \renewcommand\thehyp{\arabic{hyp}}%
  } 
  \makeatother

@@

\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}

@@

  The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then measured the similarity value for the frequency in ranked keyword lists using the Rank-biased Overlap measure. It is used for top-weighted ranked lists with different elements and lengths. We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure, both in general and only considering their common factors. More importantly, we also intend to measure how managerial and environmental attributes influence much satisfaction and dissatisfaction of both customer groups. We define managerial attributes as those internal and modifiable to the hotel. In contrast, environmental attributes are external and unmodifiable, short of moving the hotel building in its entirety.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite{Kuboyama2020}.

@@

    Therefore we pose two hypotheses for our study:

    \begin{subhyp}
    \begin{hyp}
    \label{hyp:omotenashi_zh}
    Chinese tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
    \end{hyp}

    \begin{hyp}
    \label{hyp:omotenashi_en}
    Western tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
    \end{hyp}

    However, Japanese hospitality comes from Japanese culture. Different cultures interacting with it could have a different reaction. While some might be impressed by it, some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the above hypothesis:

    \begin{hyp}
    \label{hyp:omotenashi_both}
    Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service.
    \end{hyp}
    \end{subhyp}

@@

    Therefore we propose:

    \begin{subhyp}
    \begin{hyp}
    \label{hyp:diff_all}
    Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
    \end{hyp}

    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another. Therefore, it could be that some factors do not appear in the other reviews at all. For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language. So we must measure their differences or similarities at their common ground as well. For this, we prepare the following hypothesis:

    \begin{hyp}
    \label{hyp:diff_com}
    The common factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
    \end{hyp}
    \end{subhyp}

@@

    Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}. However, little focus is put on factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

    This leads to the next hypothesis:

    \begin{hyp}
    \label{hyp:man_env}
    Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
    \end{hyp}

    The resulting proportions of managerial attributes to environmental attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.

@@

    These last three articles focus on U.S.A. culture, while our study focuses on Western culture. Another difference with our study is that of the context of the study. The first study \cite{FRANCESCO201924} has the context of tourists from 3 countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A. and Chinese tourists eating in 3 countries in Europe, and the third analyzing reviews of restaurants in Bejing. Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall? Our study measures this at a large scale across different hotels in Japan.

@@

@@

    \caption{Comparison between cross-culture or cross-country previous studies and our study}

@@

     & \textbf{Bauer et.al (1993)} & \textbf{\begin{tabular}[c]{@{}l@{}}Choi and\\ Chu (2000)\end{tabular}} & \textbf{Kim and Lee (2000)} & \textbf{Huang (2017)} & \textbf{\begin{tabular}[c]{@{}l@{}}Francesco and\\ Roberta (2019)\end{tabular}} & \textbf{Jia (2020)} & \textbf{Our study} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Comparison subjects}} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} & \begin{tabular}[c]{@{}l@{}}Anglo-Americans\\ vs \\ Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ English-speakers\end{tabular} & \begin{tabular}[c]{@{}l@{}}USA\\ vs\\ China\\ vs\\ Italy\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ US tourists\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study topic}} & Changes in demand & Satisfaction Levels & Tourist Motivation & \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} & \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} & \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and \\ Dissatisfaction\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Geographical focus}} & Asia Pacific region & Hong Kong & Global & Beijing & Multi-national & Multi-national & \textbf{Japan} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Industry}} & Hotels & Hotels & Tourism & \begin{tabular}[c]{@{}l@{}}Restaurant \\ (Beijing Roast Duck)\end{tabular} & Hotels & Restaurants & Hotels \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study subjects}} & Hotel managers & Hotel customers & \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Sample method}} & surveys & surveys & survey & text mining & text mining & text mining & text mining \\ \hline
    \multicolumn{1}{|l|}{\textbf{Number of samples}} & 185 surveys & 540 surveys & \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}9000 reviews \\ (3000 per country)\end{tabular} & \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}91,172 reviews\\ (49,561 Chinese)\\ (41,611 English)\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study method}} & statistics & VARIMAX & MANOVA & \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} & Text Link Analysis & \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}SVM and \\ Rank-biased overlap\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Subject nationality}} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Fiji, \\ Hong Kong, \\ Indonesia, \\ Malaysia, \\ Singapore, \\ Taiwan, Guam, \\ Tahiti, Thailand\\ \\ Westerners: \\ Australia, \\ New Zealand\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Taiwan, \\ Japan,\\ South Korea, \\ South-East Asia\\ \\ Westerners: \\ North America,\\ Europe, Australia, \\ New Zealand\end{tabular} & USA, Japan & \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., USA, Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} & USA, China, Italy & USA, China & \begin{tabular}[c]{@{}l@{}}Chinese-speakers: \\ China\\ \\ English speakers:\\ (U.K., USA, \\ Australia,  \\ New Zealand, \\ Canada,  Ireland)\end{tabular} \\ \hline

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that would contribute the most to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized SVM. We then observed the weight values of each keyword in the machine. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}. Finally, we used this ranking in frequency to perform a Rank-biased overlap test and make observations for the hypothesis testing.

  \begin{figure}[bp]
  \centering
  \includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
  \label{fig:method-overview}
  \end{figure}

@@

    However, we needed to make the data and comparisons we draw from each of these datasets fair. For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580} and that the overlapping date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

    We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.

    To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. The English language is full of variations and conjugations of words depending on the context and tense. Thus, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

    % Please add the following required packages to your document preamble:
    % \usepackage{graphicx}
    \begin{table}[hbp]
    \centering
    \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
    \label{tab:svm_f1_zh}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    \textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
    \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
    \begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
    \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
    \end{tabular}
    \end{table}

    \begin{table}[h] \centering
    \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
    \label{tab:svm_f1_en}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
    \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
    \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
    \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
    \end{tabular}
    \end{table}

>>>>

  \usepackage{lineno, hyperref}
  \usepackage{array, pbox}
  \usepackage{mathtools}
  \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{graphicx}

@@

  % To add research questions
  \usepackage{ntheorem}
  \theoremseparator{:}
  \newtheorem{rsq}{Research Question}

  % To add subrsq theorems
  \makeatletter
  \newcounter{subrsq} 
  \let\savedc@rsq\c@rsq
  \newenvironment{subrsq}
   {%
    \setcounter{subrsq}{0}%
    \stepcounter{rsq}%
    \edef\saved@rsq{\thersq}% Save the current value of rsq
    \let\c@rsq\c@subrsq     % Now rsq is subrsq
    \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
   }
   {}
  \newcommand{\normrsq}{%
    \let\c@rsq\savedc@rsq % revert to the old one
    \renewcommand\thersq{\arabic{rsq}}%
  } 
  \makeatother

@@

\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures}

@@

  % The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast the satisfaction and dissatisfaction factors of both customer groups using natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups. We define hard attributes as those that are difficult to change by a hotel management without investing in infrastructure or real estate. In contrast, soft attributes are easily modifiable by improvements in management.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.

@@

    Therefore we pose a research question for our study:

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:omotenashi}
    To what degree are Chinese and Western tourists satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service?
    \end{rsq}

    However, Japanese hospitality comes from Japanese culture. Different cultures interacting with it could have a different reaction. While some might be impressed by it, some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the above research question:

    \begin{rsq}
    \label{rsq:omotenashi_both}
    Do Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service?
    \end{rsq}
    \end{subrsq}

@@

    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another. Therefore, it could be that some factors do not appear in the other reviews at all. For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language. So we must measure their differences or similarities at their common ground as well.

@@

    Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}. However, little focus is put on hard factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

    This leads to another research question:

    \begin{rsq}
    \label{rsq:hard_soft}
    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel.
    \end{rsq}

    The resulting proportions of hard attributes to soft attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.

@@

    These last three articles focus on U.S.A. culture, while our study focuses on Western culture. Another difference with our study is that of the context of the study. The first study \cite{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A. and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing. Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall? Our study measures this at a large scale across different hotels in Japan.

@@

    \begin{table}[htp]

@@

    \caption{Comparison between cross-culture or cross-country previous studies and our study.}

@@

    \textbf{} &
      \textbf{Bauer et.al (1993)} &
      \textbf{Choi and Chu (2000)} &
      \textbf{Kim and Lee (2000)} &
      \textbf{Huang (2017)} &
      \textbf{Francesco and Roberta (2019)} &
      \textbf{Jia (2020)} &
      \textbf{Our study} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
      \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study topic}} &
      Changes in demand &
      Satisfaction Levels &
      Tourist Motivation &
      \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
      \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
      Asia Pacific region &
      Hong Kong &
      Global &
      Beijing &
      Multi-national &
      Multi-national &
      \textbf{Japan} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Industry}} &
      Hotels &
      Hotels &
      Tourism &
      Restaurant (Beijing Roast Duck) &
      Hotels &
      Restaurants &
      Hotels \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study subjects}} &
      Hotel managers &
      Hotel customers &
      \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Sample method}} &
      surveys &
      surveys &
      survey &
      text mining &
      text mining &
      text mining &
      text mining \\ \hline
    \multicolumn{1}{|l|}{\textbf{Number of samples}} &
      185 surveys &
      540 surveys &
      \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
      9000 reviews (3000 per country) &
      \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
      \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Study method}} &
      statistics &
      VARIMAX &
      MANOVA &
      \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
      Text Link Analysis &
      \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
      \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
      \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
      \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
      USA, Japan &
      \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
      USA, China, Italy &
      USA, China &
      \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that would contribute the most to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews, as well as a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset in price ranges to observe the satisfaction factors and their differences between different lower class hotels and higher class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel, meaning whether a hotel management can easily change those attributes, or if they are difficult to change without investing in infrastructure or real estate.

  \begin{figure}[bp]
  \centering
  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
  \label{fig:method-overview}
  \end{figure}

@@

    However, we needed to make the data and comparisons we draw from each of these datasets fair. For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. In addition, we selected only the hotels that had a pricing information available. We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well. The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel. Regardless of the reason, the highest priced room can be an indicator of the class of hotel indirectly, which can give us an insight into the kind of service that is offered. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}. The overlapping date range for reviews was from July 2014 to July 2017. Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences. We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.

    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at. We therefore made observations on the distribution of pricing in the hotels of our database and binned the data by price ranges, decided by consideration of objective of stay. We show these distributions in Figure \ref{fig:price_dist}. The structure of the data after division by price is shown in Table \ref{tab:exp_notes}, which also includes the results of emotional classification after application of our SVC, as explained in \ref{sentimentanalysis}.

    \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
            \caption{50 equal lenght bins}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
            \caption{manually set 9 price ranges}
        \end{subfigure}
    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
    \label{fig:price_dist}
    \end{figure}
